### 2015-02-22 fundamentals/fcsreqs.tex
Comments on things we say about VISION, et al
Put VISION in gls{}
tried to clean up the citation listing in IBi

The proprietary concerns of research institutions and security constraints of
data within fuel cycle simulators often restrict access. Use of a simulator is
therefore often limited to its institution of origin, necessitating effort
duplication at other institutions and thereby squandering broader human
resources. License agreements and institutional approval are required for most
current simulators (i.e. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, EVOLCODE,
FAMILY21, \gls{NFCSim})\cite{juchau_modeling_2010}, ORION, and VISION.  Even when, as in
the case of the MIT \gls{CAFCA} software, the source code is unrestricted, the
platform on which it relies is often restricted or costly.  However, \Cyclus
provides fully free and open access to all users
and developers, foreign and domestic.

>>>>

The proprietary concerns of research institutions and security constraints of
data within fuel cycle simulators often restrict access. Use of a simulator is
therefore often limited to its institution of origin, necessitating effort
duplication at other institutions and thereby squandering broader human
resources. License agreements and institutional approval are required for most
current simulators (e.g., \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, EVOLCODE,
FAMILY21, \gls{NFCSim})\cite{juchau_modeling_2010}, including ORION,
and \gls{VISION}.  Even when, as in the case of the MIT \gls{CAFCA} software,
the source code is unrestricted, the platform on which it relies is often
restricted or costly.  However, \Cyclus provides fully free and open access to
all users and developers, foreign and domestic.
